Other analysis

### 2024-06-25 analysis/misc-analysis.qmd
Add treaty actions

tar_load(map_with_data)
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))
```

@@

@@

>>>>

tar_load(c(map_with_data, action_state_type, action_treaty, action_non_derog))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))
```

# Map of derogations

@@

# Map of backsliding

@@

# Treaty actions by state and type

```{r}
#| label: fig-treaty-action-state-type
#| fig-width: 6.5
#| fig-height: 4

plot_action_state_type <- action_state_type |> 
  select(State, Total = `Treaty Action Count`, Derogation, Other) |>
  pivot_longer(cols = -State, names_to = "type", values_to = "count") |> 
  arrange(desc(type), desc(count)) |> 
  mutate(State = fct_inorder(State))

panels <- plot_action_state_type |> 
  filter(type == "Total") |> 
  mutate(panel = ifelse(row_number() <= 21, 1, 2)) |> 
  select(State, panel)

plot_action_state_type |> 
  filter(type != "Total") |> 
  left_join(panels, by = join_by(State)) |> 
  ggplot(
    aes(x = count, y = fct_rev(State), fill = fct_rev(type))
  ) +
  geom_col() + 
  scale_fill_manual(values = clrs[c(3, 6)], guide = guide_legend(reverse = TRUE)) +
  labs(x = "Total treaty actions between March 2020–June 2021", y = NULL, fill = NULL) +
  facet_wrap(vars(panel), scales = "free_y") +
  theme_pandem() +
  theme(strip.text = element_blank())
```

# Treaty actions by treaty

```{r}
#| label: tbl-treaty-action-treaty

action_treaty |> 
  mutate(Treaty = fct_reorder(Treaty, `Number of Actions`)) |> 
  group_by(`Number of Actions`) |> 
  summarize(Treaties = str_flatten(Treaty, collapse = "; ")) |> 
  ungroup() |> 
  arrange(desc(`Number of Actions`)) |> 
  tt(width = c(0.2, 0.8)) |> 
  style_tt(j = 1:2, align = "l") |> 
  style_tt(
    bootstrap_class = "table table-sm"
  )
```

```{r}
#| label: fig-treaty-action-treaty
#| fig-width: 6.5
#| fig-height: 5

action_treaty |> 
  mutate(Treaty = fct_reorder(Treaty, `Number of Actions`)) |> 
  mutate(panel = ifelse(row_number() >= 11, 1, 2)) |> 
  ggplot(aes(x = `Number of Actions`, y = Treaty)) +
  geom_col(fill = clrs[5]) +
  scale_y_discrete(labels = label_wrap(35)) +
  labs(x = "Number of actions", y = NULL) +
  facet_wrap(vars(panel), scales = "free_y") +
  theme_pandem() +
  theme(strip.text = element_blank())
```

# Non-derogation actions

```{r}
#| label: fig-treaty-non-derog
#| fig-width: 6.5
#| fig-height: 2.25

action_non_derog |> 
  mutate(Action = fct_reorder(`Treaty Action`, Count)) |> 
  ggplot(aes(x = Count, y = Action)) +
  geom_col(fill = clrs[3]) +
  labs(x = "Number of non-derogation actions", y = NULL) +
  theme_pandem()
```
